---
title: "Casual Project Test Run with optimal k"
author: "Tiankai"
date: "2023-12-5"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, load in necessary functions for this project.
```{r}
# 2018-2020 NHANES proportion (https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0255583)
# 2011-2018 NHANES proportion (https://jamanetwork.com/journals/jama/fullarticle/2784659)

library(tidyverse)
library(dplyr)

#### ---- Define Custom Functions

# function for generate optimal k
optiaml_a1a2 = function(k,mu_trial=mu_trial,mu_target=mu_target){
  #flip = (-1)^rbinom(1,1,prob = 0.5)
  a <- 0.5 - k/2
  b <- 0.5 + k/2
  
  f =  function (a1) qnorm(a1,mu_trial,1) - qnorm(2*a-a1,mu_target,1)
  optimal_a1 = uniroot(f, lower = 0, upper = min(1,2*a))$root
  a2 = a-optimal_a1
  
  return(list(k=k, a1=optimal_a1, a2=a2))
}
  
simulate_data <- function(k) {
  
  # Parameters for sample sizes
  N = 5000
  N_Trial = floor(0.5*N)
  N_Target = N - N_Trial
  
  # Parameters for differential specification
  l <- 0.5
  p <- 0.5
  
  ##### Gender ##### 
  p_male1 = 0.396 # p_male = 0.396 from NHANES
  Male_trial <- rbinom(N_Trial, 1, p_male1)
  p_male2 = 0.492
  Male_target <- rbinom(N_Target, 1, p_male2)
  
  Male = c(Male_trial, Male_target)
  
  ##### Age ##### 
  # Trial
  alpha <- 7.5
  beta <- 5.4
  Sim_age_Trial <- rbeta(N_Trial, alpha, beta)
  
  # Adjust the simulated age data to your desired age range
  min_age <- 15 
  max_age <- 80   
  Sim_age_Trial <- min_age + Sim_age_Trial * (max_age - min_age)
  
  # Target
  alpha <- 6
  beta <- 5
  Sim_age_Target <- rbeta(N_Target, alpha, beta)
  
  # Adjust the simulated age data to your desired age range
  min_age <- 18   
  max_age <- 75   
  Sim_age_Target <- min_age + Sim_age_Target * (max_age - min_age)
  
  Age = c(Sim_age_Trial, Sim_age_Target)
  
  #Race # fix Asian+other
  Race_Trial <-sample(c("Non-Hispanic White", "Non-Hispanic Black", "Hispanic", "Other"), 
                      N_Trial, replace=TRUE, prob=c(0.518, 0.239, 0.209, 0.034)) # From Obesity NHANES
  Race_Target <-sample(c("Non-Hispanic White", "Non-Hispanic Black", "Hispanic", "Other"), 
                       N_Target, replace=TRUE, prob=c(0.382, 0.237, 0.247, 0.134)) # From CVD NHANES 
  Race <- as.factor(c(Race_Trial, Race_Target))
  
  # Use model.matrix to create one-hot encoded vectors
  # The "-1" removes the intercept term
  Race_one_hot_encoded <- model.matrix(~ Race - 1, data.frame(Race)) %>% as.data.frame()
  
  # Rename the columns for clarity (optional)
  colnames(Race_one_hot_encoded) <- levels(Race)
  
  #BMI
  slope_age <- 0.6 # From NHANES
  slope_sex <- -0.425 # From NHANES
  BMI <- slope_age * Age + slope_sex * Male  + rnorm(N, mean = 0, sd = 6.5) # Males on average have lower BMI
  
  # Generate Latent Variable
  Udiff <- runif(1, -1, 1) # Size of underlying var difference between trial and target pops
  mu_trial = -Udiff*0.5
  mu_target = Udiff*0.5
  UTrial <- rnorm(N_Trial, mu_trial, 1)
  UTarget <- rnorm(N_Target, mu_target, 1)
  U = c(UTrial, UTarget)
  
  a1 = optiaml_a1a2(k=k,mu_trial=mu_trial,mu_target=mu_target)$a1
  flip = (-1)^rbinom(1,1,prob = 0.5)
  a_thresh <- flip*qnorm(a1,mu_trial,1)
  b_thresh <- -a_thresh
  VTrial <- ifelse(UTrial < a_thresh, "Low", "High")
  VTarget <- ifelse(UTarget < b_thresh, "Low", "High")
  
  # # Cut Latent Variable
  # Trial_cut_less <- rbinom(1, 1, prob = 0.5) # Binary indicator for Trial cut point less than Target cut point
  # a <- l - k/2 # l=0.5
  # b <- l + k/2
  # a_thresh <- qnorm(a)
  # b_thresh <- qnorm(b)
  # if (Trial_cut_less==1) {
  #   VTrial <- ifelse(UTrial < a_thresh, "Low", "High")
  #   VTarget <- ifelse(UTarget < b_thresh, "Low", "High")
  # } else {
  #   VTrial <- ifelse(UTrial < b_thresh, "Low", "High")
  #   VTarget <- ifelse(UTarget < a_thresh, "Low", "High")
  # }
  
  V = factor(c(VTrial, VTarget), levels = c("Low", "High"))
  
  # Create treatment and study indicator variables
  ATrial <- rbinom(N_Trial, 1, .5)
  A <- c(ATrial, rep(NA, N_Target)) # 1 if treat, 0 if control (only for those in trial!)
  S <- c(rep(1, N_Trial), rep(0, N_Target)) # indicator variable for trial
  
  # Define potential outcomes
  ATE_param = 5
  ATE <- 30 + U*ATE_param
  beta_0 <- 100
  epsilon <- 50
  beta_race <- matrix(4:1, ncol = 1)
  beta_male <- 3
  beta_age <- -.2
  beta_bmi <- 1
  beta_U <- 3
  
  effect_race <- as.matrix(Race_one_hot_encoded) %*% beta_race %>% 
    as.vector()
  
  Y0 <- beta_male * Male + beta_age * Age + beta_bmi * BMI + beta_U * U + 
    effect_race + rnorm(N, beta_0, sd = epsilon) 
  Y1 <- beta_male * Male + beta_age * Age + beta_bmi * BMI + beta_U * U + 
    effect_race + rnorm(N, beta_0, sd = epsilon) + ATE
  Y <- ifelse(A==1, Y1, Y0) # Y is NA for subjects in the target population
  data <- data.frame(Male, Age, Race, BMI, V, A, S, Y0, Y1, Y, U)
  
  ## -- Quality Assure Data
  # Check to ensure that after grouping by S and A, each Race level includes at least one observation
  N_Race <- levels(Race) %>% length()
  N_Race_by_group <- data %>% group_by(S, A) %>% count(Race) %>% group_split() %>% sapply(nrow)
  if (any(N_Race_by_group != N_Race)) { stop("After grouping by S and A, at least one level of Race has no observations.") }
  
  return(data)
}

get_tate_true <- function(data) {
  targetdata <- subset(data, S==0)
  tateTrue <- mean(targetdata$Y1-targetdata$Y0)
  return(tateTrue)
}

estimate_tates <- function(data) {
  S<-data$S
  A<-data$A
#Analyze data
  #outcome regression version
  
    #Step one: create necessary datasets
    studydata<- subset(data, S==1)
    studydataT<- subset(studydata, A==1)
    studydataC<- subset(studydata, A==0)
    targetdata <- subset(data, S==0)
    
    #Step two: make models for E[Y|X, S=1, A=a]
    treatlm <- lm(Y ~ Male+Age+Race+BMI+V, data=studydataT)
    contlm <- lm(Y ~ Male+Age+Race+BMI+V, data=studydataC)
    
    #Step 3: get predicted values for set st S=0 for both assignments
      #set A=1
        targetdata$A <- 1
        gt<-data$gt <- predict(treatlm,newdata =data)
      #set A=0
        targetdata$A <- 0
        gc<-data$gc <- predict(contlm, newdata = data)
    
    #Step 4: get E[Y^a|S=0]'s
    mut <- (1/sum((1-S)))*sum((1-S)*gt)
    muc <- (1/sum((1-S)))*sum((1-S)*gc)
    #Step 5: subtract them to get the estimated TATE
    tateOR <- mut - muc
    
    
  #IOW1
    data$p <- 1/(1+exp(-1* predict(glm(S ~ Male+Age+Race+BMI+V, data=data, family="binomial"),newdata = data)))#P(S=1|X)
    data$e1 <- 1/(1+exp(-1* predict(glm(A ~ Male+Age+Race+BMI+V, data=studydata, family="binomial"),newdata = data)))# P(A=1|X, S=1)
    data$e0 <-  1/(1+exp(-1*predict(glm((1-A) ~ Male+Age+Race+BMI+V, data=studydata, family="binomial"),newdata = data)))# P(A=0|X, S=1)
    
    data$w1<-ifelse(S==1 & A==1, (1-data$p)/(data$p*data$e1), 0)
    data$w0<-ifelse(S==1 & A==0, (1-data$p)/(data$p*data$e0), 0)
    muIOW1t <- (1/sum((1-S)))*sum(data$w1*data$Y,na.rm =T)
    muIOW1c <- (1/sum((1-S)))*sum(data$w0*data$Y,na.rm =T)
    tateIOW1 <- muIOW1t-muIOW1c
    
   #IOW2
    muIOW2t <- (1/sum(data$w1,na.rm =T))*sum(data$w1*data$Y,na.rm =T)
    muIOW2c <- (1/sum(data$w0,na.rm =T))*sum(data$w0*data$Y,na.rm =T)
    tateIOW2 <- muIOW2t-muIOW2c
    
  #DR1
    muDR1t <-  (1/sum((1-S)))*(sum(data$w1*(data$Y-gt),na.rm =T)+sum((1-S)*gt,na.rm =T))
    muDR1c <- (1/sum((1-S)))*(sum(data$w0*(data$Y-gc),na.rm =T) +sum((1-S)*gc,na.rm =T))
    tateDR1 <- muDR1t - muDR1c
    
  #DR2
    muDR2t <-  (1/sum(data$w1,na.rm =T))*sum(data$w1*(data$Y-gt),na.rm =T) +(1/sum((1-S)))*sum((1-S)*gt,na.rm =T)
    muDR2c <-  (1/sum(data$w0,na.rm =T))*sum(data$w0*(data$Y-gc),na.rm =T) +(1/sum((1-S)))*sum((1-S)*gc,na.rm =T)
    tateDR2 <- muDR2t - muDR2c
  
  tates <- c(tateOR, tateIOW1, tateIOW2, tateDR1, tateDR2)
  return(tates)
}

# Function to perform bootstrap resampling and estimate the five quantities
bootstrap_tates <- function(data, B=100) {
  
  # Number of observations
  n_obs <- nrow(data)

  # Number of estimates
  num_estimates <- 5
  
  # Matrix to store bootstrap estimates
  bootstrap_matrix <- matrix(NA, nrow = B, ncol = num_estimates)
  
  # Perform bootstrap resampling
  for (b in 1:B) {
    
    # Sample with replacement
    bootstrap_ids <- sample(1:n_obs, n_obs, replace = TRUE)
    bootstrap_sample <- data[bootstrap_ids, ]
    
    # Calculate the five estimates
    bootstrap_estimates <- estimate_tates(bootstrap_sample)
    
    # Store the estimates in the matrix
    bootstrap_matrix[b, ] <- bootstrap_estimates
  }
  
  return(bootstrap_matrix)
}

# Determine for checking if the truth is in the confidence intervals
check_inclusion <- function(ci, truth) {
  truth_included <- as.numeric(ci[1] < truth & truth < ci[2])
  return (truth_included)
}
```
```{r}
library(tictoc)
```

## ANALYSIS

Here is the base case.
```{r}
k <- 0

tic()
# Matrix for coverage indicators
M <- 50

seed = floor(20*k*M+343)

set.seed(seed)

# Number of estimates
num_estimates <- 5

true_tates <- rep(NA, M)
tate_matrix <- coverage_matrix <- confidence_interval_length_matrix <- matrix(NA, nrow = M, ncol = num_estimates) 

for (m in 1:M) {
  
  # Simulate 
  data_m <- simulate_data(k)
  # Get the truth
  tate_true_m <- get_tate_true(data_m)
  # Point estimate tates
  tates_m <- estimate_tates(data_m)
  # Bootstrap variability
  bootstrap_matrix <- bootstrap_tates(data_m)
  # Get Confidence Intervals
  confidence_intervals <- apply(bootstrap_matrix, MARGIN = 2, 
                                FUN = quantile, probs = c(0.025, 0.975)) 
  # Determine if the truth is in the confidence intervals
  coverage_indicators <- apply(confidence_intervals, MARGIN = 2, 
                               check_inclusion, tate_true_m)
  # Get Confidence Interval Length
  confidence_interval_lengths <- confidence_intervals[2, ] - confidence_intervals[1, ]
  
  # Store outputs
  true_tates[m] <- tate_true_m
  tate_matrix[m, ] <- tates_m
  coverage_matrix[m, ] <- coverage_indicators
  confidence_interval_length_matrix[m, ] <- confidence_interval_lengths
}

result_k0 <- list(true_tates, tate_matrix, coverage_matrix, confidence_interval_length_matrix)
names(result_k0) <- c("true_tates", "tate_matrix", "coverage_matrix", "confidence_interval_length_matrix")
toc() #244.52 sec elapsed
```

Display result at k=0
```{r}
result_k0
```

```{r}
Truth_W_tate = cbind.data.frame(truth = as.matrix(result_k0$true_tates,nrow=M),result_k0$tate_matrix)
Avg_truth_W_tate_k0 = colMeans(Truth_W_tate)
Avg_truth_W_tate_k0

Bias = result_k0$tate_matrix - result_k0$true_tates
Avg_bias_k0 = colMeans(Bias)
Avg_bias_k0

Avg_abs_bias_k0 = colMeans(abs(Bias))
Avg_abs_bias_k0

Avg_cov_k0 = colMeans(result_k0$coverage_matrix)
Avg_cov_k0

Avg_ci_len_k0 = colMeans(result_k0$confidence_interval_length_matrix)
Avg_ci_len_k0

Avg_res_k0 = list(Avg_truth_W_tate = Avg_truth_W_tate_k0, 
                  Avg_bias = Avg_bias_k0, Avg_abs_bias = Avg_abs_bias_k0, 
                  Avg_cov = Avg_cov_k0, Avg_ci_len = Avg_ci_len_k0)
```

Then we try to run under different k.
```{r}
#tic()
k <- 0.05

# Matrix for coverage indicators
M <- 50

seed = floor(20*k*M+343)

set.seed(seed)

# Number of estimates
num_estimates <- 5

true_tates <- rep(NA, M)
tate_matrix <- coverage_matrix <- confidence_interval_length_matrix <- matrix(NA, nrow = M, ncol = num_estimates) 

for (m in 1:M) {
  
  # Simulate 
  data_m <- simulate_data(k)
  # Get the truth
  tate_true_m <- get_tate_true(data_m)
  # Point estimate tates
  tates_m <- estimate_tates(data_m)
  # Bootstrap variability
  bootstrap_matrix <- bootstrap_tates(data_m)
  # Get Confidence Intervals
  confidence_intervals <- apply(bootstrap_matrix, MARGIN = 2, 
                                FUN = quantile, probs = c(0.025, 0.975)) 
  # Determine if the truth is in the confidence intervals
  coverage_indicators <- apply(confidence_intervals, MARGIN = 2, 
                               check_inclusion, tate_true_m)
  # Get Confidence Interval Length
  confidence_interval_lengths <- confidence_intervals[2, ] - confidence_intervals[1, ]
  
  # Store outputs
  true_tates[m] <- tate_true_m
  tate_matrix[m, ] <- tates_m
  coverage_matrix[m, ] <- coverage_indicators
  confidence_interval_length_matrix[m, ] <- confidence_interval_lengths
}

result_k0.05 <- list(true_tates, tate_matrix, coverage_matrix, confidence_interval_length_matrix)
names(result_k0.05) <- c("true_tates", "tate_matrix", "coverage_matrix", "confidence_interval_length_matrix")
#toc() #193.06 sec elapsed
```

Display result at k=0.05
```{r}
result_k0.05
```
Create average value for the results
```{r}
Truth_W_tate = cbind.data.frame(truth = as.matrix(result_k0.05$true_tates,nrow=M),result_k0.05$tate_matrix)
Avg_truth_W_tate_k0.05 = colMeans(Truth_W_tate)
Avg_truth_W_tate_k0.05

Bias = result_k0.05$tate_matrix - result_k0.05$true_tates
Avg_bias_k0.05 = colMeans(Bias)
Avg_bias_k0.05

Avg_abs_bias_k0.05 = colMeans(abs(Bias))
Avg_abs_bias_k0.05


Avg_cov_k0.05 = colMeans(result_k0.05$coverage_matrix)
Avg_cov_k0.05

Avg_ci_len_k0.05 = colMeans(result_k0.05$confidence_interval_length_matrix)
Avg_ci_len_k0.05

Avg_res_k0.05 = list(Avg_truth_W_tate = Avg_truth_W_tate_k0.05, 
                  Avg_bias = Avg_bias_k0.05, Avg_abs_bias = Avg_abs_bias_k0.05, 
                  Avg_cov = Avg_cov_k0.05, Avg_ci_len = Avg_ci_len_k0.05)
```


I also tried a different k
```{r}
#tic()
k <- 0.2

# Matrix for coverage indicators
M <- 50

seed = floor(20*k*M+343)

set.seed(seed)

true_tates <- rep(NA, M)
tate_matrix <- coverage_matrix <- confidence_interval_length_matrix <- matrix(NA, nrow = M, ncol = num_estimates) 

for (m in 1:M) {
  
  # Simulate 
  data_m <- simulate_data(k)
  # Get the truth
  tate_true_m <- get_tate_true(data_m)
  # Point estimate tates
  tates_m <- estimate_tates(data_m)
  # Bootstrap variability
  bootstrap_matrix <- bootstrap_tates(data_m)
  # Get Confidence Intervals
  confidence_intervals <- apply(bootstrap_matrix, MARGIN = 2, 
                                FUN = quantile, probs = c(0.025, 0.975)) 
  # Determine if the truth is in the confidence intervals
  coverage_indicators <- apply(confidence_intervals, MARGIN = 2, 
                               check_inclusion, tate_true_m)
  # Get Confidence Interval Length
  confidence_interval_lengths <- confidence_intervals[2, ] - confidence_intervals[1, ]
  
  # Store outputs
  true_tates[m] <- tate_true_m
  tate_matrix[m, ] <- tates_m
  coverage_matrix[m, ] <- coverage_indicators
  confidence_interval_length_matrix[m, ] <- confidence_interval_lengths
}
#toc() #206.86 sec elapsed
result_k0.2 <- list(true_tates, tate_matrix, coverage_matrix, confidence_interval_length_matrix)
names(result_k0.2) <- c("true_tates", "tate_matrix", "coverage_matrix", "confidence_interval_length_matrix")
```

Display result at k=0.2 
```{r}
result_k0.2
```
Create average value for the results above
```{r}
Truth_W_tate = cbind.data.frame(truth = as.matrix(result_k0.2$true_tates,nrow=M),result_k0.2$tate_matrix)
Avg_truth_W_tate_k0.2 = colMeans(Truth_W_tate)
Avg_truth_W_tate_k0.2

Bias = result_k0.2$tate_matrix - result_k0.2$true_tates
Avg_bias_k0.2 = colMeans(Bias)
Avg_bias_k0.2

Avg_abs_bias_k0.2 = colMeans(abs(Bias))
Avg_abs_bias_k0.2

Avg_cov_k0.2 = colMeans(result_k0.2$coverage_matrix)
Avg_cov_k0.2

Avg_ci_len_k0.2 = colMeans(result_k0.2$confidence_interval_length_matrix)
Avg_ci_len_k0.2

Avg_res_k0.2 = list(Avg_truth_W_tate = Avg_truth_W_tate_k0.2, 
                  Avg_bias = Avg_bias_k0.2, Avg_abs_bias = Avg_abs_bias_k0.2, 
                  Avg_cov = Avg_cov_k0.2, Avg_ci_len = Avg_ci_len_k0.2)
```


```{r}
#tic()
k <- 0.5

# Matrix for coverage indicators
M <- 50

seed = floor(20*k*M+343)

set.seed(seed)

true_tates <- rep(NA, M)
tate_matrix <- coverage_matrix <- confidence_interval_length_matrix <- matrix(NA, nrow = M, ncol = num_estimates) 

for (m in 1:M) {
  
  # Simulate 
  data_m <- simulate_data(k)
  # Get the truth
  tate_true_m <- get_tate_true(data_m)
  # Point estimate tates
  tates_m <- estimate_tates(data_m)
  # Bootstrap variability
  bootstrap_matrix <- bootstrap_tates(data_m)
  # Get Confidence Intervals
  confidence_intervals <- apply(bootstrap_matrix, MARGIN = 2, 
                                FUN = quantile, probs = c(0.025, 0.975)) 
  # Determine if the truth is in the confidence intervals
  coverage_indicators <- apply(confidence_intervals, MARGIN = 2, 
                               check_inclusion, tate_true_m)
  # Get Confidence Interval Length
  confidence_interval_lengths <- confidence_intervals[2, ] - confidence_intervals[1, ]
  
  # Store outputs
  true_tates[m] <- tate_true_m
  tate_matrix[m, ] <- tates_m
  coverage_matrix[m, ] <- coverage_indicators
  confidence_interval_length_matrix[m, ] <- confidence_interval_lengths
}

result_k0.5 <- list(true_tates, tate_matrix, coverage_matrix, confidence_interval_length_matrix)
names(result_k0.5) <- c("true_tates", "tate_matrix", "coverage_matrix", "confidence_interval_length_matrix")
#toc() #215.7 sec elapsed
```

Display result at k=0.5 
```{r}
result_k0.5
```

```{r}
Truth_W_tate = cbind.data.frame(truth = as.matrix(result_k0.5$true_tates,nrow=M),result_k0.5$tate_matrix)
Avg_truth_W_tate_k0.5 = colMeans(Truth_W_tate)
Avg_truth_W_tate_k0.5

Bias = result_k0.5$tate_matrix - result_k0.5$true_tates
Avg_bias_k0.5 = colMeans(Bias)
Avg_bias_k0.5

Avg_abs_bias_k0.5 = colMeans(abs(Bias))
Avg_abs_bias_k0.5

Avg_cov_k0.5 = colMeans(result_k0.5$coverage_matrix)
Avg_cov_k0.5

Avg_ci_len_k0.5 = colMeans(result_k0.5$confidence_interval_length_matrix)
Avg_ci_len_k0.5

Avg_res_k0.5 = list(Avg_truth_W_tate = Avg_truth_W_tate_k0.5, 
                  Avg_bias = Avg_bias_k0.5, Avg_abs_bias = Avg_abs_bias_k0.5, 
                  Avg_cov = Avg_cov_k0.5, Avg_ci_len = Avg_ci_len_k0.5)
```


```{r}
#tic()
k <- 0.8

# Matrix for coverage indicators
M <- 50

seed = floor(20*k*M+343)

set.seed(seed)

# Number of estimates
num_estimates <- 5

true_tates <- rep(NA, M)
tate_matrix <- coverage_matrix <- confidence_interval_length_matrix <- matrix(NA, nrow = M, ncol = num_estimates) 

for (m in 1:M) {
  
  # Simulate 
  data_m <- simulate_data(k)
  # Get the truth
  tate_true_m <- get_tate_true(data_m)
  # Point estimate tates
  tates_m <- estimate_tates(data_m)
  # Bootstrap variability
  bootstrap_matrix <- bootstrap_tates(data_m)
  # Get Confidence Intervals
  confidence_intervals <- apply(bootstrap_matrix, MARGIN = 2, 
                                FUN = quantile, probs = c(0.025, 0.975)) 
  # Determine if the truth is in the confidence intervals
  coverage_indicators <- apply(confidence_intervals, MARGIN = 2, 
                               check_inclusion, tate_true_m)
  # Get Confidence Interval Length
  confidence_interval_lengths <- confidence_intervals[2, ] - confidence_intervals[1, ]
  
  # Store outputs
  true_tates[m] <- tate_true_m
  tate_matrix[m, ] <- tates_m
  coverage_matrix[m, ] <- coverage_indicators
  confidence_interval_length_matrix[m, ] <- confidence_interval_lengths
}

result_k0.8 <- list(true_tates, tate_matrix, coverage_matrix, confidence_interval_length_matrix)
names(result_k0.8) <- c("true_tates", "tate_matrix", "coverage_matrix", "confidence_interval_length_matrix")
#toc() #223.56 sec elapsed
```

```{r}
result_k0.8
```

```{r}
Truth_W_tate = cbind.data.frame(truth = as.matrix(result_k0.8$true_tates,nrow=M),result_k0.8$tate_matrix)
Avg_truth_W_tate_k0.8 = colMeans(Truth_W_tate)
Avg_truth_W_tate_k0.8

Bias = result_k0.8$tate_matrix - result_k0.8$true_tates
Avg_bias_k0.8 = colMeans(Bias)
Avg_bias_k0.8

Avg_abs_bias_k0.8 = colMeans(abs(Bias))
Avg_abs_bias_k0.8

Avg_cov_k0.8 = colMeans(result_k0.8$coverage_matrix)
Avg_cov_k0.8

Avg_ci_len_k0.8 = colMeans(result_k0.8$confidence_interval_length_matrix)
Avg_ci_len_k0.8

Avg_res_k0.8 = list(Avg_truth_W_tate = Avg_truth_W_tate_k0.8, 
                  Avg_bias = Avg_bias_k0.8, Avg_abs_bias = Avg_abs_bias_k0.8, 
                  Avg_cov = Avg_cov_k0.8, Avg_ci_len = Avg_ci_len_k0.8)
```

## RESULT

```{r}
## result
res2vec = function(avg_res){
  dt = matrix(c(as.numeric(avg_res$Avg_truth_W_tate[-1]),
                avg_res$Avg_bias,avg_res$Avg_abs_bias, avg_res$Avg_cov,
                avg_res$Avg_ci_len), ncol=5,nrow = 5)
  vec = round(c(as.numeric(avg_res$Avg_truth_W_tate[1]),c(t(dt))),4)
  return(vec)
}

avg_vec_k0 = res2vec(Avg_res_k0)
avg_vec_k0.05 = res2vec(Avg_res_k0.05)
avg_vec_k0.2 = res2vec(Avg_res_k0.2)
avg_vec_k0.5 = res2vec(Avg_res_k0.5)
avg_vec_k0.8 = res2vec(Avg_res_k0.8)
```

```{r}
avg_tb = rbind.data.frame(avg_vec_k0,avg_vec_k0.05,avg_vec_k0.2,avg_vec_k0.5,avg_vec_k0.8)

colnames(avg_tb) = c("Truth","ATE_OR","bias_OR","Abs_bias_OR","cov_OR",
                     "CI_length_OR","ATE_IOW","bias_IOW","Abs_bias_IOW",
                     "cov_IOW","CI_length_IOW","ATE_IOW2","bias_IOW2",
                     "Abs_bias_IOW2","cov_IOW2","CI_length_IOW2","ATE_DRE1",
                     "bias_DRE1","Abs_bias_DRE1","cov_DRE1","CI_length_DRE1",
                     "ATE_DRE2","bias_DRE2","Abs_bias_DRE2","cov_DRE2",
                     "CI_length_DRE2")

rownames(avg_tb) = c("K=0","K=0.05","K=0.2","K=0.5","K=0.8")

avg_tb
```
# ```{r}
# library(xtable)
# print(xtable(avg_tb, type = "latex"))
# ```
Table1: TATE + bias + absolute bias
```{r}
## TATE + bias + absolute bias
avg_tb2 = rbind.data.frame(avg_vec_k0[-c(5,6,10,11,15,16,20,21,25,26)],
                           avg_vec_k0.05[-c(5,6,10,11,15,16,20,21,25,26)],
                           avg_vec_k0.2[-c(5,6,10,11,15,16,20,21,25,26)],
                           avg_vec_k0.5[-c(5,6,10,11,15,16,20,21,25,26)],
                           avg_vec_k0.8[-c(5,6,10,11,15,16,20,21,25,26)])

colnames(avg_tb2) = c("Truth","ATE_OR","bias_OR","Abs_bias_OR","ATE_IOW",
                      "bias_IOW","Abs_bias_IOW","ATE_IOW2","bias_IOW2",
                      "Abs_bias_IOW2","ATE_DRE1","bias_DRE1",
                      "Abs_bias_DRE1","ATE_DRE2","bias_DRE2","Abs_bias_DRE2")

rownames(avg_tb2) = c("K=0","K=0.05","K=0.2","K=0.5","K=0.8")

avg_tb2
```
Table2: CI coverage + CI length
```{r}
## CI coverage + CI length
avg_tb3 = rbind.data.frame(avg_vec_k0[c(5,6,10,11,15,16,20,21,25,26)],
                           avg_vec_k0.05[c(5,6,10,11,15,16,20,21,25,26)],
                           avg_vec_k0.2[c(5,6,10,11,15,16,20,21,25,26)],
                           avg_vec_k0.5[c(5,6,10,11,15,16,20,21,25,26)],
                           avg_vec_k0.8[c(5,6,10,11,15,16,20,21,25,26)])

colnames(avg_tb3) = c("cov_OR","CI_length_OR","cov_IOW","CI_length_IOW",
                      "cov_IOW2","CI_length_IOW2","cov_DRE1",
                      "CI_length_DRE1","cov_DRE2","CI_length_DRE2")

rownames(avg_tb3) = c("K=0","K=0.05","K=0.2","K=0.5","K=0.8")
```

Separate tables
```{r}
ATE_sub = avg_tb %>% select(Truth,ATE_OR,ATE_IOW,ATE_IOW2,ATE_DRE1,ATE_DRE2)
ATE_sub
bias_sub = avg_tb %>% select(bias_OR,bias_IOW,bias_IOW2,bias_DRE1,bias_DRE2)
bias_sub
Abs_bias_sub = avg_tb %>% select(Abs_bias_OR,Abs_bias_IOW,Abs_bias_IOW2,
                                 Abs_bias_DRE1,Abs_bias_DRE2)
Abs_bias_sub
cov_sub = avg_tb %>% select(cov_OR,cov_IOW,cov_IOW2,cov_DRE1,cov_DRE2)
cov_sub 
CI_length_sub = avg_tb %>% select(CI_length_OR,CI_length_IOW,CI_length_IOW2,
                                  CI_length_DRE1,CI_length_DRE2)
CI_length_sub
```
Here is for graphing
```{r}
library(ggplot2)
k_lst = c("0","0.05","0.2","0.5","0.8")

##### ATE ##### 
method = rep(c("Truth","OR" ,"IOW" ,"IOW2" ,"DRE1" ,"DRE2"),each = length(k_lst))
k = rep(k_lst,6)
ATE_lst = as.numeric(unlist(ATE_sub))
ATE_tb = cbind.data.frame(Method = method,K = k,ATE = ATE_lst)

ggplot(data=ATE_tb, aes(x=K, y=ATE_lst, group=Method)) +
  geom_line(aes(color=Method))+
  geom_point(aes(color=Method))+ 
  xlab("K") +
  ylab("TATE") +
  ggtitle("TATE under different Method and different K")
```
```{r}
##### Bias ##### 
method = rep(c("OR" ,"IOW" ,"IOW2" ,"DRE1" ,"DRE2"),each = length(k_lst))
k = rep(k_lst,5)
bias_lst = as.numeric(unlist(bias_sub))
bias_tb = cbind.data.frame(Method = method,K = k,bias = bias_lst)

ggplot(data=bias_tb, aes(x=K, y=bias_lst, group=Method)) +
  geom_line(aes(color=Method))+
  geom_point(aes(color=Method))+ 
  xlab("K") +
  ylab("Bias") +
  ggtitle("Bias under different Method and different K")
```
```{r}
##### Absolute Bias ##### 
method = rep(c("OR" ,"IOW" ,"IOW2" ,"DRE1" ,"DRE2"),each = length(k_lst))
k = rep(k_lst,5)
Abs_bias_lst = as.numeric(unlist(Abs_bias_sub))
Abs_bias_tb = cbind.data.frame(Method = method,K = k,Abs_bias = Abs_bias_lst)

ggplot(data=Abs_bias_tb, aes(x=K, y=Abs_bias_lst, group=Method)) +
  geom_line(aes(color=Method))+
  geom_point(aes(color=Method))+ 
  xlab("K") +
  ylab("Absolute Bias") +
  ggtitle("Absolute Bias under different Method and different K")
```

```{r}
##### Coverage ##### 
method = rep(c("OR" ,"IOW" ,"IOW2" ,"DRE1" ,"DRE2"),each = length(k_lst))
k = rep(k_lst,5)
cov_lst = as.numeric(unlist(cov_sub))
cov_tb = cbind.data.frame(Method = method,K = k,cov = cov_lst)

ggplot(data=cov_tb, aes(x=K, y=cov_lst, group=Method)) +
  geom_line(aes(color=Method))+
  geom_point(aes(color=Method))+ 
  xlab("K") +
  ylab("Coverage") +
  ggtitle("Coverage under different Method and different K")
```


```{r}
## CI length
create_long = function(result){
  Method = rep(c("OR" ,"IOW" ,"IOW2" ,"DRE1" ,"DRE2"),
               each = nrow(result$confidence_interval_length_matrix))
  CI_length = c(result$confidence_interval_length_matrix[,1],
             result$confidence_interval_length_matrix[,2],
             result$confidence_interval_length_matrix[,3],
             result$confidence_interval_length_matrix[,4],
             result$confidence_interval_length_matrix[,5])
  long_tb = cbind.data.frame(CI_length,Method)
  long_tb$Method = factor(long_tb$Method, 
                          levels = c("OR" ,"IOW" ,"IOW2","DRE1" ,"DRE2"))
  return(long_tb)
}
long_tb_k0 = create_long(result_k0)
long_tb_k0.05 = create_long(result_k0.05)
long_tb_k0.2 = create_long(result_k0.2)
long_tb_k0.5 = create_long(result_k0.5)
long_tb_k0.8 = create_long(result_k0.8)

long_tb_fivek = rbind.data.frame(long_tb_k0,long_tb_k0.05,long_tb_k0.2,
                                 long_tb_k0.5,long_tb_k0.8)
K_long = rep(paste0("k=",k_lst),each= nrow(long_tb_k0))

long_CI_len_all = cbind.data.frame(long_tb_fivek, K = K_long)

CI_plot <- ggplot(long_CI_len_all, aes(x=Method,y=CI_length,fill=Method))+
  geom_boxplot() +
  labs(title="Confidence Interval Length under different Method and different K") +facet_wrap(~K)+
  ylab("Confidence Interval Length") + theme(legend.position="bottom")
CI_plot
```